A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\bigskip
 In this work, upscaling is performed through linear regression in the PCA space which is obtained with SVD or HOSVD for 2D and 3D cases, respectively. This work focuses on reducing the order of permeability distribution in porous media flow simulations. Section~\ref{section:mathematical_model} introduces the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field. The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) \cite{Gomes_2017} which couples both the fine resolution and upscaled representation of the permeability field. Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to assess the various upscaling techniques used. Four upscaling techniques are investigated in this work and they are named Arithmetric mean, Harmonic mean, probability density function (PDF) and PCA (using SVD for 2D models and HOSVD for 3D model) coupled with linear regression.

>>>>

\bigskip
 In this work, upscaling is performed through linear regression in the PCA space which is obtained with high-order singular value decomposition (HOSVD/SVD) in 2-/3-D problems. This work focuses on reducing the order of permeability distribution in porous media flow simulations. Section~\ref{section:mathematical_model} introduces the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field. The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) \cite{Gomes_2017} which couples both the fine resolution and upscaled representation of the permeability field. Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to assess the various upscaling techniques used. Four upscaling techniques are investigated in this work and they are named Arithmetric mean, Harmonic mean, probability density function (PDF) and PCA (using SVD for 2D models and HOSVD for 3D model) coupled with linear regression.
